Health Data

### 2020-04-20 01_health_data.Rmd
Repo cleanup
This includes a number of edits to the data elements related to switching the unit of analysis from tracts to block groups

```{r setup}
library(leaflet)
library(tidyverse)
library(tidycensus)
library(RSocrata)
library(sf)
options(tigris_use_cache=TRUE)
```

>>>>

```{r setup, cache = FALSE}
knitr::opts_chunk$set(cache = TRUE)
library(leaflet)
library(tidyverse)
library(tidycensus)
library(RSocrata)
library(sf)
options(tigris_use_cache=TRUE)
```
